Learning from Data Through Models"  # nolint: Grammarly.

### 2023-09-01 Paper/draft.Rmd
11 rounds

---
title: "Learning from Data Through Models"
date: '`r format(Sys.time(), "%B %d, %Y")`'
author: "Jimena Galindo"
abstract: "TBW"
#classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
output: 
    pdf_document:
        citation_package: natbib
        fig_width: 7
        fig_height: 6
        fig_caption: true
        number_sections: true

@@

# Framework
An agent is of type $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$ and they face an unknown 
exogenous state
$\omega \in \{\omega_L, \omega_M, \omega_H\}$ with $\omega_H>\omega_M>\omega_L$. 
Each of the values of $\omega$ is realized with equal probability. The agent knows the distribution of $\omega$ but not its value. 
They also hold some prior belief about $\theta$ which is potentially misspecified.\footnote{The particular types of misspecification
that are allowed are discussed below.}
The agent chooses a binary gamble $e in \{e_L, e_M, e_H\}$ and and observes whether the gamble is a success or a failure. '
If it is a success,
the agent gets a payoff of $1$ and if it is a failure, the agent gets a payoff of $0$. The probability of success is increasing in
both $\theta$ and $\omega$ and is fully described in the following table:

@@

After observing the outcome of each gamble, the agent updates their beliefs of both theta and omega in one of 4 differente ways: 
As a \emph{dogmatic} as in @Heidhues2018 ; as a \emph{switcher} as in @Ba2023 ; as a \emph{self-attribution} updater as in @Coutts2020; 
or as a fully Bayesian agent. Each of these updating rules is described in detail below.

Notice that both \theta and \omega can be identified from the outcomes.
However, under the assumption that the agent is myopic, the choices might not gererate sufficient variation in effort to 
identify both. Such cases arise when the agent is either overconfident or underconfident about their type and the combination
of their choices with the exogenous state are such that the data observed is consistent with the erroneous beliefs. Each of 
the updating mecahnisms above will make different predicitons about the cases in which the agent is able to learn their true 
type and when the misspecification persists.

>>>>

---
title: "Learning from Data Through Models"  # nolint: Grammarly.
date: '`r format(Sys.time(), "%B %d, %Y")`'
author: "Jimena Galindo"
abstract: "TBW"
#classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
output: 
    pdf_document:
        citation_package: natbib
        fig_width: 7
        fig_height: 6
        fig_caption: true
        number_sections: true

@@

# Framework
An agent is of type $\theta \in \{\theta_L, \theta_M, \theta_H\}$  with $\theta_H > \theta_M > \theta_L$ and they face an unknown 
exogenous state
$\omega \in \{\omega_L, \omega_M, \omega_H\}$ with $\omega_H>\omega_M>\omega_L$. 
Each of the values of $\omega$ is realized with equal probability. The agent knows the distribution of $\omega$ but not its value. 
They also hold some prior belief about $\theta$ which is potentially misspecified.\footnote{The particular types of misspecification
that are allowed are discussed below.}
The agent chooses a binary gamble $e in \{e_L, e_M, e_H\}$ and observes whether the gamble is a success or a failure. '
If it is a success,
the agent gets a payoff of $1$ and if it is a failure, the agent gets a payoff of $0$. The probability of success is increasing in
both $\theta$ and $\omega$ and is fully described in the following table:

@@

After observing the outcome of each gamble, the agent updates their beliefs of both theta and omega in one of 4 different ways: 
As a \emph{dogmatic} as in @Heidhues2018 ; as a \emph{switcher} as in @Ba2023 ; as a \emph{self-attribution} updater as in @Coutts2020; 
or as a fully Bayesian agent. Each of these updating rules is described in detail below.

Notice that both \theta and \omega can be identified from the outcomes.
However, under the assumption that the agent is myopic, the choices might not generate sufficient variation in effort to 
identify both. Such cases arise when the agent is either overconfident or underconfident about their type and the combination
of their choices with the exogenous state is such that the data observed is consistent with the erroneous beliefs. Each of 
the updating mechanisms above will make different predictions about the cases in which the agent can learn their true 
type and when the misspecification persists.
